\documentclass{article}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=0.5in}

\pagestyle{fancy}
\fancyhf{} % clear all header fields
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\copyright\;aquarc 2024. \href{https://aquarc.org}{\underline{aquarc.org}}} % other info in "inner" position of footer line

\title{\vspace{-3em}New Intern Info\vspace{-3em}}

\begin{document}

\fontsize{14}{16}\selectfont

\maketitle\thispagestyle{fancy}
\vspace{-40pt}

\section{Introduction}

You signed up for the internship at \href{https://aquarc.org}{\underline{aquarc}}. Here's every step of the process and what you need to know if you join the team.

\section{Who we are looking for}

We are looking for people with a burning desire to create something new. Put simply, \href{https://aquarc.org}{\underline{aquarc}} aims to be an all-in-one platform encompassing the entire high school education. Right now, we have SAT help, an extracurricular finder, and a weekly internship newsletter. \\

Although it's perfectly valid to be joining the team if you want to add items to your resume, the main driving force we want to see is passion and desire for a change. These are the people that tend to \textbf{stick the longest through the hardest times}. And like any early stage startup, that's exactly what we are looking for.

\section{Your Position}

The purpose of the interview is to decide where you would best fit into the team, \textbf{if} you are to be selected. \\

You most likely fit into one of these categories:

\begin{itemize}
    \item Working on the app, frontend or backend. Tech Development Intern
    \item Writing the infrastructure for the tech developers. Systems Intern (DevOps)
    \item Marketing the product through YouTube videos/shorts/Insta reels.
    \item You make study materials or questions, or maybe find more internships/extracurriculars.
\end{itemize}

That's not to say you \textbf{have} to fit into one of those categories. These aren't rigid, just what we are working on right now. \\

So are you an intern? An employee? A volunteer? Actually, all of them!

\begin{itemize}
    \item Intern: Definitely an \textbf{immersive} learning experience. You're going to learn teamwork, development, and quick adaptation in a startup by getting thrown right into the heat of it.
    \item Employee: You're going to have responsibilities, just like any person. You'll have to step in from time to time to help make ends meet.
    \item Volunteer: Everything that you're going to work on is 100\% free for \textbf{all users} or you will get compensated otherwise. We want to make aquarc as accessible and useful as possible and \textbf{we won't put anything you work on behind a paywall.}
\end{itemize}

So instead of thinking of your position as a rigid internship from a specified start date to end date, you're really being chosen to join us for the ride. This opportunity is \textbf{what you make out of it.} \\

If you're looking purely to add another item to your resume, we don't want you. This company and your position is \textbf{something new.}

\section{Logistics}

All communications happen via the \href{https://signal.org}{\underline{Signal Messenger App}}. The first thing you'll have to do is download the app and add my number: 609-721-9242. \\

Send your resume to \href{mailto:contact@aquarc.org}{\underline{contact@aquarc.org}} with a 3 sentence cover letter. This task \textbf{is optional}, but strongly recommended. \\

You're going to have either one or two rounds of straightforward interviews.

\section{Interview Prep}

We value \textbf{honesty and responsibility} over everything else. \\

Be prepared to explain how exactly you want to help out at aquarc and what you want to learn while you are here. This desire can change over time; just emphasize what you are looking for right now and what you think you want to do in the future. \\

More importantly, explain how you will stay committed and consistent even when results don't show. As you're most likely in school, you have to manage a school-work balance as well. Be prepared to show how that would work. \\

In addition to the information you provide, we will help you manage your time and develop motivation skills during and after the interview. Here are some sample questions we might ask:

\begin{itemize}
    \item What makes you feel valued?
    \item What kind of training would you like from your job?
    \item What subjects do you need the most help with at school?
\end{itemize}

\section{On The Team}

Every Sunday. 3PM EST, there's a meeting. If you can't come, explain why you can't. These meetings are designed to help you improve your thinking and keeping the core team close, both of which are very important in any startup. \\

Time management is odd for most, if not all high schoolers. We are here to help. You'll be working odd hours like weekends and nights. However, every small step of progress you make will be visible growth for aquarc. 

We expect about a 10-12 hours of work per week time commitment. Don't take this numbet at face value; we are here to work out how exactly everything will work during your interview. We can give you strategies like using a timer or sorting your priorities, but it is ultimately up to you to implement them. \textbf{Remember, this opportunity is exactly what you make of it.}\\

Again, your honesty and integrity are very important. The last thing we want is you saying that you can do something and giving you a responsibility and you being inable to fulfill it due to bad planning.

\section{Our Plans}

Note these may be slightly out of date.

For tech team: join our \href{https://trello.com/invite/b/673964cad256125abd5d1d70/ATTIecbb1e9c31e9dba725dadbb4781edf8aB68D0D76/aquarc-tech}{\underline{trello}} \textbf{if and only if you're selected}. \\

For marketing, we want to make YouTube videos to establish our credibility and take a few sections and make reels with those. Consistent posting will not only gain us visibility, but trust. \\

For study materials and questions, we just want to be consistent in what we are making.

\section{Terms and Conditions}

You are \textbf{not entitled} to compensation for your work. You \textbf{may or may not} receive a position with a salary at the end of your work. You will not be asked to work in the \textbf{for-profit LLC sector} pursuant to the Fair Labor Standards Act. You'll only work for the \textbf{501(c)(3) sector}. \\

You consent to aquarc using your code, writings, or other materials for the benefit of high schoolers.

\section{Conclusion}

If you made it to the end, congrats! You definitely care about what you're doing, at the least. \\

If you have any questions, shoot us an email at \href{mailto:contact@aquarc.org}{\underline{contact@aquarc.org}}.

\end{document}
