\documentclass{article}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=0.5in}

\pagestyle{fancy}
\fancyhf{} % clear all header fields
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\copyright\hspace{0.5em}aquarc 2024. \href{https://aquarc.org}{\underline{aquarc.org}}} % other info in "inner" position of footer line

\title{\vspace{-3em}Essay\vspace{-3em}}

\begin{document}

\fontsize{14}{16}\selectfont

\maketitle\thispagestyle{fancy}
\vspace{-20pt}

\begin{center}
    In a 2016 interview published in the Los Angeles Review of Books, Maxine Hong Kingston, an award-winning writer famous for her novels depicting the experiences of Chinese immigrants in the United States, stated: “I think that individual voices are not as strong as a community of voices. If we can make a community of voices, then we can speak more truth.” \\

    Write an essay that argues your position on the extent to which Kingston’s claim about the importance of creating a community of voices is valid. \\

    In your response you should do the following:

    \begin{itemize}
        \item  Respond to the prompt with a thesis that presents a defensible position.
        \item Provide evidence to support your line of reasoning.
        \item Explain how the evidence supports your line of reasoning.
        \item Use appropriate grammar and punctuation in communicating your argument.
    \end{itemize}

    \copyright \hspace{0.2em} 2023 College Board
\end{center}

\section{Planning}
\hspace{1em}Kingston is trying to say that what more people agree with is correlates to more truth. Since each person has unique beliefs and a unique version of the truth, taking the common and arguing the differences will come to a more universal version of the truth. \\

If I had to take a side, I would say that this statement is true only to the point where science takes over. For example, for centuries people believed that the Earth was the cen- ter of the solar system. When astronomers tried to prove otherwise, they were silenced. However, the ”community of voices” would argue the lie rather than the truth. \\

An argument against would be the subjectivity of truth. ”Ice cream is bad” could be a perfectly valid version of the truth for some people and the opposite can hold true for other people. The question would require us to define truth itself in the Introduction. \\

For the sake of simplicity, let’s define truth as an idea or belief that cannot be argued
against given present scientific evidence. That should make the claim easier to prove.

\section{Skeleton Outline}

\subsection{Intro}
\begin{itemize}
    \item Truth is an idea that can’t be disproved in the presence of scientific evidence. It is subjective.
    \item Truth can be wildly different from what people think.
    \item Kingston’s statement is valid until scientific evidence proves otherwise.
\end{itemize}

\subsection{Body Paragraphs}

\begin{itemize}
    \item Topic sentence: people may gatekeep the truth for their own interests
    \item Evidence: Cite the example of the astronomers hidden behind the church.
    \item Topic sentence: People may not know information
    \item Evidence: People didn’t know about the dangers of risky investing until they got hit
    \item  it and a lot continued thinking it was ”true” to have a bull market forever.
    \item Topic sentence: Where truth is subjective, then voices win
    \item Hitler blamed Germany's problems on Jews but that wasn't true
\end{itemize}

\section{Essay}

\hspace{1em}Truth appears to be subjective. It differs from person to person and can vary widely in different settings. Kingston argues that a universal truth can be attained by leveraging a "community of voices." This community may not always correlate to truth, however, because truth can't be disproved in the face of scientific evidence. Therefore Kingston's claim is true where science cannot be used because the largest sample size of people will always hold the most versions of truth; but if science can prove or disprove an objective truth, Kingston's claim doesn't hold. \\

Scientific evidence may not always be accessible, which is what happens when people hide the truth for their own interests. A few centuries ago, in Europe people and the church held that the sun and all extraterrestrial objects revolved around Earth. When an astronomer observed the movement and proved otherwise, he was locked up for his ideas so the church could maintain power. In this scenario the church hid the truth to safeguard its interests, by ensuring what they say remains the people's truth which proves their legitimacy. The truth in this scenario is the objective fact that the sun revolves around the Earth, even though the "community of voices" would argue otherwise, disproving Kingston's claim. Sometimes human power or emotions can get in the way of access to the truth. \\

Human emotions obscure the truth in the face of scientific evidence. Prior to the 1929 Great Depression, spending increased and people thought the economy would continue to boom. After major railroads went bankrupt and cut back on employment, the economy failed and the reality of business cycles moving in boom and bust phases comes to light. In this scenario access wasn't deliberately hidden, but positive emotions and hope obscured the truth, making people think that "bust" cycles of the economy were over. The "community of voices" actually went further from the truth because of all the hype surrounding stocks and investments, disproving Kingston's claim in the light of evidence. Objective truths have no correlation with people. \\

In contrast to objective truths, subjective truths do correlate with people and reinforce Kingston's claim. Prior to the Holocaust, the Nazis attempted to root out Germany's problems. They placed the blame of these problems on Jews in an attempt to unify the nation. Since scientific evidence cannot determine the "cause of the war", using information from Jews and general people in addition to the Nazis would shine light on a clearer reality where the differing opinions would help define the problem and unify in an alternative and better way. This "community of voices" would give rise to a more truthful and beneficial implementation plan for Germany, reinforcing Kingston's claim on the importance of multiple voices. \\

Since truth can be both objective and subjective, scientific evidence and the voices of the people have to be used in conjunction to determine what's true and what's not, which disproves Kingston's idea of a universla truth. Truth depends from person to person and can widely depend in different scenarios because it's not a rigidly defined idea.

\end{document}
